Problem 1
We installed PeacoQC during this session, but we didn’t have time to explore what functions are present within the package. Using what you have learned about accessing documentation, figure out and list what functions it contains
```{r}
library(PeacoQC)
?PeacoQC
```

Problem 2
Take a closer look at the list of Bioconductor cytometry packages. Report back on how many there are currently in Bioconductor, the author/maintainer with the most contributed cytometry R packages, and a couple packages that you would be interested in exploring more in-depth later in the course.

```{r}
#I saved a screenshot in the folder showing how many cytometry related packages I found.

#One of the most active contributors appears to be the RGLab developer group, which maintains several core cytometry packages such as flowCore, flowWorkspace, openCyto, CytoML, and ggcyto. I would be interested in exploring further CytoML for FlowJo integration

```
 
Problem 3
There is another way to install R packages, using the newer pak package. Positron uses this when installing suggested dependencies.

After learning more about it via the documentation and it’s pkgdown website, I would like you to attempt to install the following three R packages using this newer method: “broom”, “cytoMEM”, “DillonHammill/CytoExploreR”.

Take screenshots, and in a new quarto markdown document, describe how the installation process differed from what you saw for install.packages(), install() and install_github().


```{r}
install.packages("pak")
library(remote)
library(pak)

pak::pkg_install("broom")
pak::pkg_install("cytoMEM")
pak::pkg_install("DillonHammill/CytoExploreR")

#I actually didn´t find it so different, to me, it looks like it took more time to install but it also showed how was going the installation step by step

#I could not install CytoExploreR by pak but it was possible with the install_github

remotes::install_github("DillonHammill/CytoExploreR")

```