Problem 1
Using flowGate, go ahead and create your own series of gates for either our data or your own for any cell populations that might interest you. Once done, save the GatingSet, and then successfully reload it. Add another gate, but intentionally misdraw it. Then proceed to visualize, identify and correct it, before saving again.

If you do plan to switch over to R for gating long-term, these skillsets will be essential, as you will need to be confident in your ability to adjust your gates as needed.

```{r}
PATH_TO_PAC_46_48_fcs <-  file.path("course", "08_WaysToGate", "homeworks", "biancakbeck")
PATH_TO_PAC_46_48_fcs

PAC_46_48_fcs <- list.files(PATH_TO_PAC_46_48_fcs, pattern = ".fcs", full.names = TRUE)
PAC_46_48_fcs
library(flowCore)

swab_46_f <- PAC_46_48_fcs[2]
swab_46_f

read.FCS(filename = swab_46_f, transformation = FALSE, truncate_max_range = FALSE)

flowFrame <- read.FCS(filename=swab_46_f, transformation = FALSE, truncate_max_range = FALSE)


MFI_Matrix <- flowFrame@exprs
MFI_Matrix_Alternate <- exprs(flowFrame)
head(MFI_Matrix, 5)
ColumnNames <- colnames(MFI_Matrix)
ColumnNames
str(ColumnNames)
class(ColumnNames)
unname(ColumnNames)

#renaming the columns
colnames(MFI_Matrix )
colnames(MFI_Matrix)[5]
colnames(MFI_Matrix)[5] <- "SpikePositive"
colnames(MFI_Matrix)[6] <- "CD27Positive"
colnames(MFI_Matrix)[7] <- "IgMPositive"
colnames(MFI_Matrix)[8] <- "DUMP"
colnames(MFI_Matrix)[9] <- "CD19Positive"
colnames(MFI_Matrix)[10] <- "LIVE"
colnames(MFI_Matrix)[11] <- "CD138Positive"

colnames(MFI_Matrix)[13] <- "CD38Positive"

colnames(MFI_Matrix)[15] <- "IgAPositive"
colnames(MFI_Matrix)[16] <- "IgDPositive"
colnames(MFI_Matrix )

#ws
flowset <- read.flowSet(files = PAC_46_48_fcs , truncate_max_range = FALSE, transformation = FALSE)
flowset

library(flowWorkspace)
cytoframe <- load_cytoframe_from_fcs(PAC_46_48_fcs[2], truncate_max_range = FALSE, transformation = FALSE)

cytoframe

SwabFiles_F <- PAC_46_48_fcs[stringr::str_detect(PAC_46_48_fcs, "Fenotipagem_SWAB")]
SwabFiles_F

SFC_cytoset <- load_cytoset_from_fcs(SwabFiles_F, truncate_max_range = FALSE, transformation = FALSE)
SFC_GatingSet <- GatingSet(SFC_cytoset)
SFC_GatingSet
pData(SFC_GatingSet)



SFC_cytoset <- load_cytoset_from_fcs(SwabFiles_F, truncate_max_range = FALSE, transformation = FALSE)
SFC_GatingSet <- GatingSet(SFC_cytoset)
SFC_GatingSet
pData(SFC_GatingSet)

Metadata <- pData(SFC_GatingSet)
str(Metadata)

#plotting
ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="FSC-A", y="SSC-A")) + geom_hex(bins=100)
 str(SFC_GatingSet[1])
#para ver se ja tem transformações
gh_get_transformations(SFC_GatingSet[1])
colnames(SFC_GatingSet)
markernames(SFC_GatingSet)


#all
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="FSC-A", y="SSC-A")) + geom_hex(bins=100)

#singlets
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="FSC-A", y= "FSC-H")) + geom_hex(bins=100)

#live
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="SSC-A", y= "BV510-A")) + geom_hex(bins=100)

#B cells
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="BV421-A", y= "APC-Cy7-A")) + geom_hex(bins=100)

#Memory and Plasm
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="BV421-A", y= "APC-A")) + geom_hex(bins=100)

#IgD-
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="PE-Cy7-A", y= "SSC-A")) + geom_hex(bins=100)

#isotype
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="PE-A", y= "A680-A")) + geom_hex(bins=100)

 #s+
  ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="Alexa Fluor 488-A", y= "BV421-A")) + geom_hex(bins=100)

#to star transforming

  gh_get_transformations(SFC_GatingSet[[1]])

 Logicle <- logicle_trans()
str(Logicle)

Biexponential <- flowjo_biexp_trans()
str(Biexponential)

Asinh <- flowjo_fasinh_trans()
str(Asinh)

#to take only the fluorophores
SFC_Parameters <- colnames(SFC_GatingSet)
SFC_Parameters
FluorophoresOnly <- SFC_Parameters[!stringr::str_detect(SFC_Parameters, "FSC|SSC|Time")]
FluorophoresOnly

#transformer list
MyBiexTransform <- transformerList(FluorophoresOnly, Biexponential)
MyBiexTransform

#just to check and take the number of channel range, max value, pos, neg and widthbasis
str(MyBiexTransform[1:3])
str(MyBiexTransform$`APC-A`)

#taking out of my ram memory, making a gating set, in the function flowjo_biexp_trans putting the numbers that i got from str() function, this numbers that i will change to transform my data, and combining those with the transformer list that we want and reaplying to the gating set
 SFC_cytoset <- load_cytoset_from_fcs(PAC_46_48_fcs,
 truncate_max_range = FALSE, transformation = FALSE)
SFC_GatingSet <- GatingSet(SFC_cytoset)
Biexponential <- flowjo_biexp_trans(
  channelRange = 4096,
  maxValue = 262144,
  pos = 3.8,
  neg = 0.5,
  widthBasis = -10)
MyBiexTransform <- transformerList(FluorophoresOnly, Biexponential)
transform(SFC_GatingSet, MyBiexTransform)

#B cells
 ggcyto(SFC_GatingSet[1], subset="root",
 aes(x="APC-Cy7-A", y= "BV421-A")) + geom_hex(bins=100)

#gating
library(remotes)
library(pak)
library(flowWorkspace)
library(ggplot2)
library(ggcyto)
library(openCyto)
library(flowGate)
library(flowCore)

colnames(SFC_GatingSet)

GatingTable <- tibble::tribble(
  ~filterId,   ~dims,                         ~subset,

  "cells",     list("FSC-A", "SSC-A"),       "root",

  "singlets",  list("FSC-A", "FSC-H"),       "cells",

  "live",      list("SSC-A", "BV510-A"),     "singlets",

  "Bcells",    list("BV421-A", "APC-Cy7-A"), "live",

  "Memory",    list("BV421-A", "APC-A"),     "Bcells",

  "Plasma",    list("BV421-A", "APC-A"),     "Bcells"
)
GatingTable
SFC_cytoset <- load_cytoset_from_fcs(SwabFiles_F,
 truncate_max_range = FALSE, transformation = FALSE)
SFC_GatingSet <- GatingSet(SFC_cytoset)

SFC_Parameters <- colnames(SFC_GatingSet)
FluorophoresOnly <- SFC_Parameters[!stringr::str_detect(SFC_Parameters, "FSC|SSC|Time")]

Biexponential <- flowjo_biexp_trans(channelRange=4096, maxValue=262144,
     pos=4.5, neg=2, widthBasis=-500)
MyBiexTransform <- transformerList(FluorophoresOnly, Biexponential)
transform(SFC_GatingSet, MyBiexTransform)

gs_apply_gating_strategy(SFC_GatingSet, gating_strategy = GatingTable)

SavePath <- file.path(  "course",  "08_WaysToGate", "homeworks",  "biancakbeck",  "MyGatingSet")
SavePath

save_gs(  SFC_GatingSet,  path = SavePath)

Reloaded_GS <- load_gs(  path = SavePath)
Reloaded_GS

#adding a wrong gate
flowGate::gs_gate_interactive(gs=Reloaded_GS, filterId="Wrong_cells", sample=1,
dims=list("PE-A", "APC-A"), subset="Bcells")

ggcyto(  Reloaded_GS[1],  subset = "live",  aes(x = "PE-A", y = "APC-A")) +  geom_hex(bins = 100) +  geom_gate("Wrong_cells")

#removing
gs_pop_remove(  Reloaded_GS,  "Wrong_cells")

#correcting
CorrectGate <- flowGate::gs_gate_interactive(gs=Reloaded_GS, filterId="correctCells", sample=1,
dims=list("PE-A", "APC-A"), subset="Bcells")
ggcyto(  Reloaded_GS[1],  subset = "live",  aes(x = "PE-A", y = "APC-A")) +  geom_hex(bins = 100) +  geom_gate("correctCells")

save_gs(  Reloaded_GS,  path = SavePath)

#to me, it looks like i could not transform correctly, and then I cant see my cell populations clearly, I would love if you could help me with that
```


Problem 2
Go ahead and create your own openCyto gate template, extending to whatever cell target population of interest. Visualize the differences, and ensure that the gates are correctly applied for everyone. Set gate_constaint arguments as needed until everything is just right.

If you do plan to switch over to R for gating long-term, these skillsets will be essential, as you will need to be confident in your ability to adjust your gates as needed.

```{r}
library(openCyto)

GateTemplate <- tibble::tribble(
~alias, ~pop, ~parent, ~dims, ~gating_method, ~gating_args, ~collapseDataForGating, ~groupBy, ~preprocessing_method, ~preprocessing_args, ~pp_res,

"problem2_cells", "+", "root", "FSC-A,SSC-A", "flowClust.2d", NA, FALSE, NA, NA, NA, NA,

"problem2_singlets", "+", "problem2_cells", "FSC-A,FSC-H", "singletGate", NA, FALSE, NA, NA, NA, NA,

"problem2_live", "-", "problem2_singlets", "BV510-A", "mindensity", "gate_range=c(0,3000)", FALSE, NA, NA, NA, NA,

"problem2_Bcells", "+", "problem2_live", "BV421-A,APC-Cy7-A", "flowClust.2d", "K=2", FALSE, NA, NA, NA, NA
)

TemplatePath <- file.path("course", "08_WaysToGate", "homeworks", "biancakbeck", "MyOpenCytoTemplate.csv")

write.csv(GateTemplate, TemplatePath, row.names = FALSE)

gt <- gatingTemplate(TemplatePath)

gt_gating(gt, SFC_GatingSet)

ggcyto(SFC_GatingSet, aes(x="FSC-A", y="SSC-A")) +
geom_hex(bins=100) +
geom_gate("problem2_cells")

ggcyto(SFC_GatingSet, subset="problem2_cells", aes(x="FSC-A", y="FSC-H")) +
geom_hex(bins=100) +
geom_gate("problem2_singlets")

ggcyto(SFC_GatingSet, subset="problem2_singlets", aes(x="BV510-A")) +
geom_density() +
geom_gate("problem2_live")

ggcyto(SFC_GatingSet, subset="problem2_live", aes(x="BV421-A", y="APC-Cy7-A")) +
geom_hex(bins=100) +
geom_gate("problem2_Bcells")
facet_wrap(~name)

#I needed alot of AI help on this one

```


Problem 3
Re-run your openCyto template, but then add a few additional flowGate on to to extend it further. Save the gating set, close out of positron, and successfully reload.


```{r}
flowGate::gs_gate_interactive(gs = SFC_GatingSet, filterId =  "problem3_IgApositive", sample = 1, dims = list("PE-A", "SSC-A"),subset = "problem2_Bcells")

ggcyto(SFC_GatingSet, subset="problem2_Bcells", aes(x="PE-A", y="SSC-A")) +geom_hex(bins=100) + geom_gate("problem3_IgApositive")

SavePath <- file.path("course","08_WaysToGate","homeworks","biancakbeck","Problem3_GatingSet")

save_gs(SFC_GatingSet, path = SavePath)

Reloaded_GS <- load_gs(path = SavePath)
gs_get_pop_paths(Reloaded_GS)
ggcyto(Reloaded_GS, subset="problem2_Bcells", aes(x="PE-A", y="SSC-A")) +geom_hex(bins=100) +
geom_gate("problem3_IgApositive")
```