Problem 1
Taking a dataset (either todays or one of your own), work through the column-operating functions (select(), rename(), and relocate()). Once this is done, filter() by conditions from two separate columns, arrange in an order that makes sense, and export this “tidy” data as a .csv file.

```{r}
#opening
getwd()
FilePath<- file.path("course", "04_IntroToTidyverse", "homeworks", "biancakbeck", "PAC_46_48.csv")
list.files(FilePath)
Data <- read.csv2(FilePath, check.names=FALSE)

#reading
class(Data)
colnames(Data)
rownames(Data)
head(Data, 3)
View(Data)
str(Data)

library(dplyr)
#select
Cells <- select(Data, "#Cells")
Cells

#relocate
Subset <- Data |> select("Name", "#Cells")
head(Subset, 3)
Data |> relocate(Depth, .after="#Cells") |> head(3)

#filter
P46 <- Data |>  filter(grepl("PBMC_046", Name))

head(P46)

#rename
RenamedP46 <- P46 |> rename( Cells = '#Cells')
colnames(RenamedP46)

#saving
DataP46 <- paste0("RenamedP46", ".csv")
StorageLocation <- file.path("course", "04_IntroToTidyverse", "homeworks", "biancakbeck", DataP46)
StorageLocation
write.csv(RenamedP46, StorageLocation, row.names=FALSE)

```

Problem 2
We used the mutate() function to create new columns, but it can also be used to modify existing ones. Various numeric columns are showing way to many significant digits. As was shown, use round() to round all these proportion columns, but use mutate to overwrite the existing column. Export this as it’s own .csv file.

```{r}
library(dplyr)
P46_Rounded <- RenamedP46 |> mutate(Statistic = round(Statistic, 1))
P46_Rounded
head(P46_Rounded)

P46_Rounded_csv <- paste0("P46_Rounded", ".csv")
StorageLocation <- file.path("course", "04_IntroToTidyverse", "homeworks", "biancakbeck", P46_Rounded_csv)
StorageLocation
write.csv(P46_Rounded_csv, StorageLocation, row.names=FALSE)
```

Problem 3
We can also use mutate() to combine columns. For our dataset, “bid”, “timepoint”, “Condition” are separate columns that originally were all part of the filename for the individual .fcs file. Try to figure out a way to combine them back together using paste0(), and save the new column as “filename”. Once this is done, pull() the contents of this column, and using try to determine whether there were any duplicates (think innovative ways of using !, length() and unique())

```{r}
library(dplyr)

# load dataset
Dataset <- read.csv(  "C:/Users/biihb/Documents/Cytometry_R/CytometryInR/course/04_IntroToTidyverse/data/Dataset.csv")

Dataset_FileNames <- Dataset |>  mutate(    filename = paste0(bid, "_", timepoint, "_", Condition, ".fcs") )

head(Dataset_FileNames)

filenames <- Dataset_FileNames |>  pull(filename)
filenames

length(filenames)

length(unique(filenames))

# TRUE = existem duplicatas
# FALSE = não existem duplicatas
duplicates_exist <- !(  length(filenames) == length(unique(filenames)))

duplicates_exist
```